\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity in Human Brains}

### 2014-01-17 docs/paper/paper final.tex
plaatjes in 2x3 opgedeeld ipv 3x2 zodat ze wat beter zichtbaar zijn O:-)

\begin{figure}[h!]
  \centering
  \includegraphics[height=0.28\textwidth]{images/new/struct_subj1-crop}
  \includegraphics[height=0.28\textwidth]{images/new/struct_subj2-crop}
  \includegraphics[height=0.28\textwidth]{images/new/struct_subj3_colorbar-crop} % one colorbar at the top right of the figure
  \includegraphics[height=0.28\textwidth]{images/new/struct_subj4-crop}
  \includegraphics[height=0.28\textwidth]{images/new/struct_subj5-crop}
  \includegraphics[height=0.28\textwidth]{images/new/struct_subj6-crop}
  \caption{The structure of all six subjects as found with the PC algorithm. The two diagonal lines represent connections between the two hemispheres.}
\label{fig:struct_subjects}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj1_expl-crop}
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj2_expl-crop}
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj3_expl-crop}
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj4_expl-crop}
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj5_expl-crop}
  \includegraphics[height=0.25\textwidth]{images/new/assym_subj6_expl-crop}
  \caption{The assymetric parts of the PDAG found with EMS-PC for all six subjects, in which a high value denotes a high certainty of a one-directional arrow.}
\label{fig:asym_subjects}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[height=0.29\textheight]{images/new/struct_subj1-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj2_colorbar-crop} % one colorbar at the top right of the figure
  \includegraphics[height=0.29\textheight]{images/new/struct_subj3-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj4-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj5-crop}
  \includegraphics[height=0.29\textheight]{images/new/struct_subj6-crop}
  \caption{The structure of all six subjects as found with the PC algorithm. The two diagonal lines represent connections between the two hemispheres.}
\label{fig:struct_subjects}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=0.26\textheight]{images/new/assym_subj1_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj2_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj3_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj4_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj5_expl-crop}
  \includegraphics[height=0.26\textheight]{images/new/assym_subj6_expl-crop}
  \caption{The assymetric parts of the PDAG found with EMS-PC for all six subjects, in which a high value denotes a high certainty of a one-directional arrow.}
\label{fig:asym_subjects}
\end{figure}
